Suplementary Material 3: Run Simulations on the Last Birth Omited Data

### 2023-04-10 S3_run_simulations_EE_not_last.Rmd
simulation running explanations

The memory (RAM) and usage is quite high for simulations. Below there are some information about the RAM  usages per  CPU of simulations on Estonian data w/o last birth. The total number of CPUs used for running these simulations was 51. RAM usage varied between models but stayed around 18 GB per CPU core (dumped cores had a size range from 12 to 23GB).

>>>>

The memory (RAM) usage is quite high for simulations. The total number of CPUs used for running single simulation on Estonian data w/o last birth was 51. RAM usage varied between models but stayed around 18 GB per CPU core (dumped cores had a size range from 12 to 23GB).
